\documentclass[../main.tex]{subfiles}

\begin{document}
\pagebreak
\section{Introduction}
This is the project report for \textit{Arcemii}. Shortly put: Arcemii is a multiplayer rogue-like app for android.

Arcemii came to be, mainly because of one reason: there wasn't anything like it yet. The idea was planted over a year ago. During the summer break before this year, Steven and Thijs wanted to play something with their friends, something with a lot of replayability. We looked for multiplayer rogue-likes, but could not find any. Summer ended, the university started, but this idea remained. Now with this course, \textit{Research and Development}, it was finally time to realize it!

\bigbreak\noindent
Above, the term `Rogue-like' is mentioned often, and it will be mentioned even more frequently later on. But what is a `Rogue-like'?  According to Wikipedia: \textit{Roguelike is a subgenre of role-playing video game characterized by a dungeon crawl through procedurally generated levels, turn-based gameplay, tile-based graphics, and permadeath of the player character, mostly with a fantasy narrative.}

So, Arcemii is a game where you go through randomly generated levels, killing fiends along the way. However, few rogue-likes have a proper multiplayer mode. This serves as the spot Arcemii has to fill. Alongside that, we want the game to be able to be played in short bursts, like in the break of a lecture. We hope to create something people can jump into easily and can bring them quick enjoyment. 

The demographic we aim at, therefore, consists of people who would like to play a game on their phone with friends. Maybe they normally game on a dedicated system or their pc, but we want to bring that experience, alongside the chaotic fun of multiplayer games, to their phones.


\end{document}